% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
\geometry{a4paper, top=0.2in, bottom=0.1in} % Set paper size and top and bottom margins
% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large XINYANG HUANG}\\[2pt] 
London, UK | \href{mailto:huangxinyangapp@163.com}{vincenthuang23@163.com} | (+44) 7810638952 | \href{https://www.linkedin.com/in/xinyang-huang/}{linkedin.com} | \href{https://github.com/D1Vincenzo}{github.com} 
\end{center}


% Experience Section
% Direct Drive
\section*{EXPERIENCE}
\noindent
\textbf{Direct Drive Technology} \hfill Guangdong, China\\ 
\textit{Research and Development Engineer Intern} \hfill Aug 2023 | Sep 2023 (On-site), Oct 2023 | Mar 2024 (Remote)
\begin{itemize}
    \item Designed and refined the generative models for UI systems on hardware interfaces, utilizing QT and Python. 
    \item Engineered and evaluated prototype demos, detailing their underlying mechanisms with Fusion 360.
    \item Engaged collaboratively in the full project lifecycle - from requirements gathering and system design to development, testing, and deployment.
    \item Monitored project timelines, addressing technical challenges as they arose to ensure adherence to deadlines.
    \item Authored comprehensive documentation, including detailed technical specifications and user guides, to support project delivery and maintenance.
% SIASUN
\end{itemize}
\noindent
\textbf{SIASUN Robot \& Automation Co., Ltd} \hfill Jiangsu, China\\ 
\textit{Mobile Robot Project Assistant Intern} \hfill Jul 2023 | Aug 2023  
\begin{itemize}
    \item Spearheaded the installation and calibration of robotic systems, significantly enhancing operational efficiency. 
    \item Conducted data collection and analysis, contributing to the development of high-precision robotic functionalities.
    \item Contributed to the resolution of technical challenges, ensuring robots performed optimally for essential operations.
\end{itemize}


% Education Section
\section*{EDUCATION}
% Master
\noindent
\textbf{University College London}, London, UK \hfill  Incoming Sep 2024 |  Sep 2025\\ 
Medical Robotics and Artificial Intelligence MSc \hfill Offer Accepted
\begin{itemize}
    \item \textbf{Major Courses:}  Robotic Systems Engineering, MSc Research Project, Artificial Intelligence for Surgery and Intervention, Medical Robotics and Devices, Surgical Data Science
\end{itemize}

% UCL
\noindent
\textbf{University College London}, London, UK \hfill  Sep 2021 |  Jun 2024\\ % University name and location
Mechanical Engineering BEng, Minor in Computer Science \hfill Expected First-Class Honours (Average Mark: 70+) % Degree and GPA
\begin{itemize}
    \item \textbf{Major Courses Studied:}  Mathematical Modelling and Analysis, Control and Instrumentation, Programming (Python), Thermodynamics, Fluid Mechanics, Engineering Dynamics, Mechanics of Solid and Structures, Materials, Manufacturing and Designs (CAD Design) 
    \item \textbf{Minor in Computer Science:} Programming (Python), Data Science (HTML, CSS, SQL, Flask, Plotly Dash), Applied Software Engineering
    \item \textbf{3rd Year Module:} Dynamics and Control, Advanced Thermodynamics and Fluid Mechanics, Elasticity and Plasticity, Undergraduate Individual Project, Project Management
    \item \textbf{3rd Year Individual Project: \textit{Enhanced Robotic Navigation Using Multi-sensor Fusion}} Elevating indoor robot navigation by fusing LiDAR with camera technology, utilizing ROS2, SLAM, and OpenCV. Aiming to overcome LiDAR's limitations in detecting close-to-floor obstacles. Programming language used are C++ and Python
\end{itemize}



% Projects Section
\section*{COMPETITIONS \& PROJECTS}
% Mechathon
\noindent
\textbf{UCL Mechathon Competition 2023} \hfill London, UK\\ 
\textit{Leader, CAD builder, Operator}  \hfill Jan 2023 \\
Sponsored by Autodesk and organized by UCL, the Competition brought together 16 teams to design and build a working robotic prototype of Hydraulic cranes within a 36-hour limit.
\begin{itemize}
    \item Awarded Silver Medal among 16 competing teams
    \item Independently designed and built the CAD model using Fusion 360.
\end{itemize}
% Hackathon
\noindent
\textbf{JP Morgan Chase \& Co. Code for Good Hackathon} \hfill London, UK\\
\textit{Front-end Engineer} \hfill Oct 2022\\
Build an NLP-powered search engine for animal testing alternatives using SpaCy and Facebook AI Similarity Search libraries in 48-hour limit.
\begin{itemize}
    \item Implemented interactive features using Bootstrap 5, HTML5, JavaScript, and CSS3, ensuring a responsive and intuitive user experience.
    \item Contributed to the project's strategy by aligning the development goals with FRAME (an organization)'s mission.
\end{itemize}
% Voice control robot project
\noindent
\textbf{Voice-Control Robot Program} \hfill Jun 2023\\
Develop a Python-based program for robot voice control, integrating speech-to-text functionalities and machine learning models for efficient real-time command output. 
\begin{itemize}
    \item Built a custom training module for enhancing voice command recognition, and a word embedding script to facilitate natural language understanding in robotic applications. 
    \item This program is fully tested on Ubuntu ROS2 and MacOS.
\end{itemize}



% Skills section
\section*{SKILLS}
\itab{\textbf{Python:} Proficient} \tab{}  \tab{\textbf{ROS:} Proficient}
\\ \itab{\textbf{C++:} Beginner} \tab{}  \tab{\textbf{MATLAB \& Simulink:} Proficient} 
\\ \itab{\textbf{JavaScript:} Beginner} \tab{}  \tab{\textbf{Fusion 360:} Proficient} 
\\ \itab{\textbf{Git:} Proficient} \tab{}  \tab{\textbf{HTML \& CSS:} Proficient} 
\\ \itab{\textbf{Mandarin:} Native} \tab{}  \tab{\textbf{English:} Proficient} 




% End document
\end{document}
